---
title: "[Disease] Surveillance Summary"
subtitle: "[Jurisdiction] — [Year Range]"
date: today
date-format: "MMMM D, YYYY"
author: "[Analyst Name]"

# ── Parameters ────────────────────────────────────────────────────────────────
# Use params to run this report for different diseases or jurisdictions without
# editing the prose. Render with a custom parameter from R:
#
#   quarto::quarto_render(
#     "scripts/05_report.qmd",
#     execute_params = list(disease = "Gonorrhea", year = 2024)
#   )

params:
  disease: "Gonorrhea"
  year: 2024

# ── Output ────────────────────────────────────────────────────────────────────
format:
  html:
    toc: true
    toc-depth: 2
    embed-resources: true   # single self-contained file; easy to email
    theme: cosmo
  docx:
    toc: true               # remove this block if Word output isn't needed

# ── Output directory ──────────────────────────────────────────────────────────
# Rendered file will land in 06_output_docs/ when rendered from the project root.
output-file: "surveillance_report.html"

# ── Execution options ─────────────────────────────────────────────────────────
execute:
  echo: false     # hide code in report; set to true for a methods appendix
  warning: false
  message: false
---

```{r}
#| label: setup

library(tidyverse)
library(here)
library(gtsummary)
library(flextable)

devtools::load_all(here::here())

# Load pre-computed analytic results
rates_by_year      <- readRDS(here("04_output_data", "rates_by_year.rds"))
rates_by_county    <- readRDS(here("04_output_data", "rates_by_county.rds"))
counts_by_age_sex  <- readRDS(here("04_output_data", "counts_by_age_sex.rds"))
counts_by_race_eth <- readRDS(here("04_output_data", "counts_by_race_eth.rds"))

current_year  <- params$year
disease_label <- params$disease

total_cases <- rates_by_year |>
  filter(epiyear == current_year) |>
  pull(n_cases)

current_rate <- rates_by_year |>
  filter(epiyear == current_year) |>
  pull(rate_per_100k)
```

## Overview

In `r current_year`, **`r format(total_cases, big.mark = ",")`** cases of
`r disease_label` were reported in [Jurisdiction], for an overall incidence rate of
**`r current_rate` per 100,000 population**.

> **Suppression note:** Counts fewer than 5 are suppressed (`*`) in all tables and
> figures to reduce the risk of re-identification.

---

## Trends Over Time

```{r}
#| label: fig-trend
#| fig-cap: !expr paste(disease_label, "incidence rate per 100,000 population,", min(rates_by_year$epiyear), "–", max(rates_by_year$epiyear))

ggplot(rates_by_year, aes(x = epiyear, y = rate_per_100k)) +
  geom_line() +
  geom_point(size = 2) +
  scale_x_continuous(breaks = rates_by_year$epiyear) +
  labs(x = "Year", y = "Rate per 100,000") +
  theme_minimal()
```

---

## Demographics

### By Age and Sex

```{r}
#| label: fig-pyramid
#| fig-cap: !expr paste(disease_label, "cases by age group and sex,", current_year)

pyramid_data <- counts_by_age_sex |>
  filter(!is.na(sex)) |>
  mutate(n_plot = if_else(sex == "Male", -n_cases, n_cases))

ggplot(pyramid_data, aes(x = n_plot, y = age_group, fill = sex)) +
  geom_bar(stat = "identity") +
  scale_x_continuous(labels = abs) +
  scale_fill_manual(values = c("Male" = "#4E79A7", "Female" = "#F28E2B")) +
  labs(x = "Number of Cases", y = "Age Group", fill = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

### By Race/Ethnicity

```{r}
#| label: tbl-race
#| tbl-cap: !expr paste(disease_label, "cases by race/ethnicity,", current_year)

counts_by_race_eth |>
  mutate(n_display = if_else(is.na(n_cases_public), "*", as.character(n_cases_public))) |>
  select(`Race/Ethnicity` = race_eth, `Cases` = n_display, `%` = pct) |>
  flextable() |>
  autofit()
```

---

## Geographic Distribution

```{r}
#| label: tbl-county
#| tbl-cap: !expr paste("Top 10 counties by", disease_label, "rate per 100,000,", current_year)

rates_by_county |>
  slice_max(rate_per_100k, n = 10) |>
  mutate(n_display = if_else(is.na(n_cases_public), "*", as.character(n_cases_public))) |>
  select(`County FIPS` = county_fips,
         `Cases`       = n_display,
         `Rate per 100,000` = rate_per_100k) |>
  flextable() |>
  autofit()
```

---

## Methods Note

Incidence rates were calculated as cases per 100,000 population using
[Census / ACS] population estimates. Epidemiological year is defined by the
CDC epidemiological week of diagnosis date. Counts fewer than 5 are suppressed.

*Report generated `r Sys.Date()` using R `r paste(R.version$major, R.version$minor, sep = ".")` and Quarto.*
