---
title: "Paper Ball Toss - Collaborative Analysis"
output: html_notebook
---

```{r setup}
renv::restore()  # restore packages to the recorded state
if(FALSE)
{
  {
    # renv::install("zoo") # istall a new package
    renv::update()   # check for upgraded packages
    renv::snapshot() # record the packages we have installed
    renv::status()
  }
}

library(readxl)
library(here)
library(summarytools)
library(dplyr)
library(tidyr)
library(here)
library(ggplot2)
```

# Collect Data

Copy the data into the project

```{r}
raw_data_dir <- here("02_raw_data/")

# "paper_ball_toss.xlsx" original data
# "paper_ball_toss_v2.xlsx" remove extra rows
raw_data_path <- file.path(raw_data_dir, "paper_ball_toss_v2.xlsx")
```
# Load raw data

```{r}
toss_raw <- read_xlsx(raw_data_path)
```

# Data Cleaining 

## Review raw data

```{r}
summary(toss_raw)
```

```{r}
toss_raw |> 
  dfSummary() |> 
  stview()
```

## Clean `participant_id`

```{r}
toss_clean <- toss_raw |>
  # To rename columns:
  rename(
    # NEW NAME       = OLD NAME
    # participant_id = variable_name_here
  ) |>
  mutate(
    participant_id = case_when(
      participant_id=="AN" ~ "ANN",
      participant_id=="MD" ~ "MB",
      participant_id=="N DC" ~ "NDC",
      .default = participant_id
    )
  ) |>
  # mutate(
  #   # fill in missing set numbrer by counting
  #   # cumulative number of times we've seen the current participant's id
  #   # set_num = rep(c(1, 2, 3), each=8*3) 
  # ) |>
  mutate(
    # fill in missing values of participant
    # participant_id = as.factor(participant_id),
    participant_id = zoo::na.locf(participant_id)
    
  ) |>
  select(
    -target_cell
  ) |>
  rename(
    toss_score = zone_score
  )
```


# Exporatory Data Analysis 

## Univariate summaries and plots 

```{r}
toss_clean |> dfSummary() |> 
  stview()
```

## Bivariate summaries and plots

```{r}
ggplot(toss_clean, aes(x = participant_id, y = toss_score)) +
  geom_boxplot() +
  geom_jitter(
    color="orange", 
    size=1, 
    alpha=0.5, 
    width=0.25,
    height=0.1,
  )
```
## Multivariate Summaries and Visualizations


```{r}
ggplot(
  toss_clean, 
  aes(
    x = factor(set_num), 
    y = toss_score,
    # color = factor(toss_in_set)
  ) 
) +
  geom_boxplot() +
  geom_jitter(
    size=1, 
    alpha=0.5, 
    width=0.25,
    height=0.1,
    aes(
      color = factor(toss_in_set),
      )
  ) +
  facet_wrap(
    vars(participant_id)
  ) +
  scale_shape_manual(
    values = c("1", "2", "3")
    )
```

# Calculate Total Score for Each Participant

```{r}
total_score <- toss_clean |>
  group_by(participant_id) |>
  summarise(
    mean_score  = mean(toss_score),
    std_score   = sd  (toss_score),
    total_score = sum (toss_score)
  ) |>
  ungroup() |>
  arrange(-total_score)
```

```{r}
total_score
```

# Does the order in the rotation impact total score?

```{r}
toss_scores <- toss_clean |>
  left_join(total_score, by = "participant_id") |>
  group_by(set_num, participant_id) |>
  filter( row_number() == 1) |>
  ungroup() |>
  group_by(set_num) |>
  mutate(
    rank = row_number()
  ) |>
  ungroup() |>
  group_by(participant_id) |>
  summarise(
    total_score  = first(total_score),
    average_rank = mean(rank)
  )

```

```{r}
toss_scores
```

```{r}
plot(
  total_score ~ average_rank, data=toss_scores
)
cor(toss_scores$total_score, toss_scores$average_rank)
```

```{r}
fit <- lm(total_score ~ average_rank, data = toss_scores)
summary(fit)
```

```{r}
x <- 10
y <- 20


fun <- function(x, y=1, z="a") {
  
  if(missing(y))
    cat("y is missing\n")
  
  for(iteration in 1:3)
  {
    cat("x=",x,"\n")
    cat("y=",y,"\n")
    cat("z=",z,"\n")
    cat("\n")
  }
}

fun(2, z="b")


```
```{r}
# Show the current searched environments
search()

# fetch a variable from a specific environment
get_var <- function(df, column_name)
{
  df[[column_name]]
}

get_var(iris, "Species")


```
# Create a function to calculate total score 
```{r}
total_scores <- function(df_scores, high=c("better", "worse"))
{
  high <- match.arg(high)
  if(!is.data.frame(df_scores))
    stop("Expected a data frame object for `df_scores")

  required_cols <- c("participant_id", "set_num", "toss_in_set", "toss_score")
  if(all(required_cols %in% colnames(df_scores)) == FALSE) {
    missing_cols <- !(required_cols %in% colnames(df_scores))
    missing_names <- required_cols[missing_cols]
    stop("Missing necessary columns: ", 
         paste("'", missing_names, "'", 
               sep='', 
               collapse=", "
               )
         )
  }
  
  retval <- df_scores |>
    left_join(total_score, by = "participant_id") |>
    group_by(set_num, participant_id) |>
    filter( row_number() == 1) |>
    ungroup() |>
    group_by(set_num) |>
    mutate(
      rank = row_number()
    ) |>
    ungroup() |>
    group_by(participant_id) |>
    summarise(
      total_score  = first(total_score),
      average_rank = mean(rank)
    ) 
  
  if (high == "better") {
    retval <- retval |> arrange(desc(total_score))
  } else if (high=="worse")
  {
    retval <- retval |> arrange(total_score)
  } else
  {
    stop("Invalid value for `high` specified:", high)
  }
  # otherwise don't change the order
    
  
  return(retval)
}
```

```{r}
try(
  # Don't stop: this is an intentional errro
  total_scores(toss_clean, "low")
)
```


```{r}
total_scores(toss_clean, "b")
```


```{r}
total_scores(toss_clean, "w")
```

```{r}
try(
  total_scores(7)
)
```
```{r}
try(
  {
    bad_df <- data.frame()
    total_scores(bad_df)
  }
)
```



